Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-02 Experiments.tex
5.2 and 5.3 --  refine and reduce

This experiment is similar to the one presented above but, in this case, we want
to test also the impact of submitting multiple generations of % new
AthenaMP to the same pilot.\mtnote{we used `generations' at the beginning of 6,
I am assuming the reader understands the term by now. Please change if you
disagree.}\aanote{I agree}
% instances in place of those that end.
% The reason behind this experiment is to
In this way, we stress the pilot's components, % by pushing new tasks while others are ending their execution
as new tasks are scheduled for execution on the Agent while other tasks are still running.

\mtnote{we do
we need to keep it below 2 hours?}\aanote{You are right. It was misleadind. I Changed. Check if you like it.}
% decided to send for execution a number of AthenaMP instances equal to
We performed the experiment by running five AthenaMP instances per node. % and w
Since we are focusing on the overhead generated by the scheduling and bootstrap of AthenaMP instances, we also reduced  the number of events simulated by each AthenaMP to sixteen in such a way that the running time of each AthenaMP is, on average, $\sim 20$ minutes.
This choice has been made to avoid the wasting of Titan's core hours but it does not affect the aim of the experiment.  
% \footnote{Note that the number of events has been chosen in such a way
% that all the cores of a node run one event.}
%In this way, every core of each worker node was used to simulate one event,
%. This allows us to complete
%reducing the running time of each AthenaMP to ~$20$ minutes. % only.

We tested
% different
pilots
% sizes, i.e. :
with 256, 512, 1024 and 2048 worker nodes and
%. For all of them, the walltime was
3\mtnote{2?} hours walltime. Figure~\ref{fig:weakScal2a} depicts the average
pilot duration, the average execution time of five sequential
generations\mtnote{generations?}\aanote{Changed} of AthenaMP, and the corresponding overhead. We
% can
observe that the difference between the two durations is more marked than in the
previous experiments \mtnote{mostly due to the increased overhead?}\aanote{Well, I guess that's plain.}. Despite this, we can notice that the growth of the overhead is consistent with the increment of the number of tasks per node for pilots with 256, 512 and 1024 worker nodes, and much less than linear for the pilot with 2048 worker nodes \aanote{Although that histogram is not trustworty because it is generate with only two runs.}

@@

The last experiments % deals with
study strong scalability by running the same amount of tasks for different pilot sizes. We used
% a number of AthenaMP instances equal to
2048 AthenaMP instances and % tested
pilots with 256, 512, 1024 and 2048 nodes. Thus, the number of AthenaMP generations is equal to eight times the size of the smallest pilot and corresponds to the size of the largest pilot. As a consequence, the number of consecutive generations of AthenaMP decreases with the pilot size by generating different dynamics within the pilots. This experiment aim to show that the pilot overhead is not affected by the concurrency level within the pilot but it depends only on the number of tasks.  
\mtnote{Not sure I understand this sentence}\aanote{My fault. It should have been seven and null or 8 and 1. It depends on how we consider the word sequential. anyway, to avoid confusion I changed the sentence.}. Each AthenaMP instance
simulates sixteen events as in the previous experiment.

>>>>

The NGE provides an important new capability of submitting multiple
generations of AthenaMP to the same pilot. In order to investigate the cost of
doing so, we performed a variant of the weak scalability experiments. This
stresses the pilot's components, as new tasks are scheduled for execution on
the Agent while other tasks are still running.

\mtnote{we dowe need to keep it below 2 hours?}\aanote{You are right. It was misleadind. I Changed. Check if you like it.}

In these experiments, we run five AthenaMP instances per node.  As these
experiments are designed to investigate the overhead generated by the
scheduling and bootstrap of AthenaMP instances, we reduced the number of
events simulated by each AthenaMP task to sixteen in such a way that the
running time of each AthenaMP is, on average, $\sim 20$ minutes. This
experiment design choice does not affect the  objectives or accuracy of the
experiments, but allows us to scale experiments to large node counts by being
conservative with allocation.

% \footnote{Note that the number of events has been chosen in such a way
% that all the cores of a node run one event.}
%In this way, every core of each worker node was used to simulate one event,
%. This allows us to complete
%reducing the running time of each AthenaMP to ~$20$ minutes. % only.

We ran
% different
pilots
% sizes, i.e. :
with 256, 512, 1024 and 2048 worker nodes and
%. For all of them, the walltime was
3\mtnote{2?} hours walltime. Figure~\ref{fig:weakScal2a} depicts the average
pilot duration, the average execution time of five sequential
generations\mtnote{generations?}\aanote{Changed} of AthenaMP, and the corresponding overhead. We
% can
observe that the difference between the two durations is more marked than in the
previous experiments \mtnote{mostly due to the increased overhead?}\aanote{Well, I guess that's plain.}. Despite this, we notice that the growth of the overhead is consistent with the increment of the number of tasks per node for pilots with 256, 512 and 1024 worker nodes, and much less than linear for the pilot with 2048 worker nodes \aanote{Although that histogram is not trustworty because it is generate with only two runs.}

@@

The last experiments % deals with
study strong scalability by running the same number of tasks for different pilot sizes. We used
2048 AthenaMP instances and % tested
pilots with 256, 512, 1024 and 2048 nodes. Thus, the number of AthenaMP generations is equal to eight times the size of the smallest pilot and corresponds to the size of the largest pilot. As a consequence, the number of consecutive generations of AthenaMP decreases with the pilot size by generating different dynamics within the pilots. These experiments are designed to investigate whether pilot overhead is affected by the degree of concurrency within the pilot and/or the number of tasks.  
\mtnote{Not sure I understand this sentence}\aanote{My fault. It should have been seven and null or 8 and 1. It depends on how we consider the word sequential. anyway, to avoid confusion I changed the sentence.}. Each AthenaMP instance
simulates sixteen events as in the previous experiment.
